True versus apparent shapes of astrophysical bow shocks

### 2017-02-06 papers/Paper1/sec-conic.tex
Rewrote Section 4 of paper to solve consistency issues.
- The conic parameters (a,b) are both defined as positive to avoid
conflicts with equation for Rc.
- THe rest of the section needs a revision.

%Instead of the excentricity, we utilize the parameter $\theta_c$ to characterize the different curves, where
%$\tan\theta_c = \frac{b}{a}$,  $b$ and $a$ are the typical parameters of conics. A positive value for $\theta_c$ indicates that the given curve is a closed one, i.e
%an ellipse, while a negative value indicates that is an hyperbola. %Insert figures if neccesary  
\begin{figure*}
\setlength\tabcolsep{0pt}
\begin{tabular}{ll}
  (a) & (b) \\
  \includegraphics[height=0.45\linewidth]{figs/ellipse_py}
      & \includegraphics[height=0.45\linewidth]{figs/hyperbola_py}
\end{tabular}
\label{fig:conics}
\caption{Example off-center conic sections that can form quadrics of
  revolution: (a) ellipse, (b) hyperbola.  The relationship is shown
  between the conic section parameters \(a\), \(b\), \(\theta_c\) and
  the bowshock characteristic radii \(R_0\), \(R_{90}\), \(R_c\), as
  defined in Fig.~\ref{fig:characteristic-radii}. The center of the
  conic is located at a distance $x_0=R_0-a$ from the origin along the
  $x$ axis.  }
\end{figure*}
\begin{figure}
\includegraphics[width=\linewidth]{conic1}
\caption{Example of a family of conic sections, all with the same
  radius of curvature at their apex (marked by white dot) on the
  \(x\)~axis: \(R_c = 2 R_0\). The parameter
  $\theta_c = \pm \tan^{-1} b/a$ describes the family, with negative
  values corresponding to hyperbolae.}
\label{fig:conics-family}
\end{figure}

Due to the similarities between the parametrization of the ellipse and the hyperbola, we can do the following parametrization
\footnote{Equations (\ref{eq:par-x}) to (\ref{eq:b-prime}) does not apply for paraboloids. Instead, the parametrization and the
  projected shape are developed in appendix \ref{app:parabola}}:
\begin{align}
x &= a\Cos(t)-x_0 \label{eq:par-x}\\ 
y &= b\Sin(t) \label{eq:par-y}
\end{align}
where:
\begin{align}
\Cos(t) &= \left\lbrace \begin{array}{c}
\cos t ~\mathrm{if~ellipse} \\
\cosh t ~\mathrm{if~hyperbola}
\end{array}\right.\\
\Sin(t) &= \left\lbrace \begin{array}{c}
\sin t ~\mathrm{if~ellipse} \\
\sinh t ~\mathrm{if~hyperbola}
\end{array}\right. \\
-\pi < t < \pi \\
R_0 &= a - x_0 \\
a<0 ~ \mathrm{for~hyperbola}
\end{align}
We have set a whole family of curves with a singular parameter denoted as $\tan\theta_c \equiv \frac{b}{a}$. Positive values of this parameter describe closed curves
(i.e. ellipses) and the negative ones describe open curves (i.e. hyperbolas). Particular cases are $\theta_c =\frac{\pi}{4}$, which describes a circle and $\theta_c=0$, which describes
a parabola.
To determine uniquely a given conic in terms of measurable quantities, we use the set of characteristic radii $(R_0,R_c,R_{90})$ in such way the conic parameters $(a,b,\theta_c)$
could be derived from the former. The transformation between the conic parameters and the characteristic radii are given by:
\begin{align}
R_c &= \frac{b^2}{a} \label{eq:Rc-conic}\\ 
R_{90} &= b\left[\pm\left(1 - \frac{(R_0-a)^2}{a^2}\right)\right]^{1/2}\label{eq:r90-conic}
\end{align}
In (\ref{eq:r90-conic}), the positive sign correspond to an elliptic quadric, while the negative sign to an hyperbolic quadric. The inverse transformation of (\ref{eq:Rc-conic})
and (\ref{eq:r90-conic}) is given by:
\begin{align}
\frac{a}{R_0} &= \frac{A}{2A-B^2} \label{eq:a-conic}\\
\frac{|b|}{R_0} &= \frac{A}{\left|2A-B^2\right|^{1/2}}\\
\tan\theta_c &= \frac{2A-B^2}{\left|B^2 - 2A\right|^{1/2}} \label{eq:thc-conic} \\
\mathrm{where:~} B &\equiv \frac{R_{90}}{R_0} \\
A &\equiv \frac{R_c}{R_0}
\end{align}

>>>>

%Instead of the excentricity, we utilize the parameter $\theta_c$ to characterize the different curves, where
%$\tan\theta_c = \frac{b}{a}$,  $b$ and $a$ are the typical parameters of conics. A positive value for $\theta_c$ indicates that the given curve is a closed one, i.e
%an ellipse, while a negative value indicates that is an hyperbola. %Insert figures if neccesary  
\begin{figure*}
\setlength\tabcolsep{0pt}
\begin{tabular}{ll}
  (a) & (b) \\
  \includegraphics[height=0.45\linewidth]{figs/ellipse_py}
      & \includegraphics[height=0.45\linewidth]{figs/hyperbola_py}
\end{tabular}
\label{fig:conics}
\caption{Example off-center conic sections that can form quadrics of
  revolution: (a) ellipse, (b) hyperbola.  The relationship is shown
  between the conic section parameters \(a\), \(b\), \(\theta_c\) and
  the bowshock characteristic radii \(R_0\), \(R_{90}\), \(R_c\), as
  defined in Fig.~\ref{fig:characteristic-radii}. The center of the
  conic is located at a distance $x_0=a \mp R_0$ from the origin along the
  $x$ axis. Where the minus sign on $R_0$ correspond to ellipses and the plus
  sign to hyperbolas}
\end{figure*}
\begin{figure}
\includegraphics[width=\linewidth]{conic1}
\caption{Example of a family of conic sections, all with the same
  radius of curvature at their apex (marked by white dot) on the
  \(x\)~axis: \(R_c = 2 R_0\). The parameter
  $\theta_c = \pm \tan^{-1} b/a$ describes the family, with negative
  values corresponding to hyperbolae.}
\label{fig:conics-family}
\end{figure}

Due to the similarities between the parametrization of the ellipse and the hyperbola, we can do the following parametrization
\footnote{Equations (\ref{eq:par-x}) to (\ref{eq:b-prime}) does not apply for paraboloids. Instead, the parametrization and the
  projected shape are developed in appendix \ref{app:parabola}}:
\begin{align}
x &= a\Cos(t)-x_0 \label{eq:par-x}\\ 
y &= b\Sin(t) \label{eq:par-y}
\end{align}
where:
\begin{align}
\Cos(t) &= \left\lbrace \begin{array}{c}
\cos t ~\mathrm{if~ellipse} \\
-\cosh t ~\mathrm{if~hyperbola}
\end{array}\right.\\
\Sin(t) &= \left\lbrace \begin{array}{c}
\sin t ~\mathrm{if~ellipse} \\
\sinh t ~\mathrm{if~hyperbola}
\end{array}\right. \\
-\pi &< t < \pi \\
R_0 &= a - x_0 \\
\end{align}
Where $a$ and $b$ are real, positive numbers.

We have set a whole family of curves with a singular parameter denoted as:
\begin{align}
  \tan\theta_c \equiv \pm\frac{b}{a}\label{eq:Thc}
\end{align}
Positive values of this parameter describe closed curves (i.e. ellipses) and the negative ones describe open curves (i.e. hyperbolas).
Particular cases are $\theta_c =\frac{\pi}{4}$,
which describes a circle and $\theta_c=0$, which describes a parabola.
To determine uniquely a given conic in terms of measurable quantities, we use the set of characteristic radii $(R_0,R_c,R_{90})$ in such way the conic
parameters $(a,b,\theta_c)$ could be derived from the former. Either way, the radius of curvature can be computed as:

\begin{align}
R_c = \frac{b^2}{a} \label{eq:Rc-conic}
\end{align}

For the rest of the parameters, the equation for ellipses and hyperbolas are very similar, except for a sign in some terms. In all cases, the upper sign will
correspond to ellipses and the lower sign for hyperbolas:

\begin{align}
R_{90} = b\left[\pm \left(1-\left(a\mp R_0\right)^2\right)\right]^{1/2}\label{eq:conic-R90}
\end{align}

Now, we can invert equations (\ref{eq:Rc-conic}) and (\ref{eq:conic-R90}) to estimate the parameters $a$ and $b$.
But first is useful to define the quantities $A \equiv \frac{R_c}{R_0}$ and $B\equiv \frac{R_{90}}{R_0}$ for simplification purposes.

\begin{align}
  \frac{a}{R_0} &= \frac{A}{\pm\left(2A-B^2\right)} \label{eq:a-con}\\
  \frac{b}{R_0} &= \frac{A}{\left|2A-B^2\right|^{1/2}} \label{eq:b-con}
\end{align}

Dividing equations (\ref{eq:a-con}) and (\ref{eq:b-con}) and substituting into equation (\ref{eq:Thc}) we get:

\begin{align}
\tan\theta_c = \frac{2A-B^2}{\left|2A-B^2\right|^{1/2}} \label{eq:th_c}
\end{align}

Note that the term $2A-B^2$ acts as a discriminant which determine the quadric we are working with.

%The transformation between the conic parameters and the characteristic radii are given by:
%\begin{align}
%R_c &= \frac{b^2}{a} \\
%R_{90} &= b\left[\pm\left(1 - \frac{(a \mp R_0)^2}{a^2}\right)\right]^{1/2}\label{eq:r90-conic}
%\end{align}ut 
%In (\ref{eq:r90-conic}), the positive sign correspond to an elliptic quadric, while the negative sign to an hyperbolic quadric.
%The inverse transformation of (\ref{eq:Rc-conic}) and (\ref{eq:r90-conic}) is given by:
%\begin{align}
%\frac{a}{R_0} &= \frac{A}{2A-B^2} \label{eq:a-conic}\\
%\frac{|b|}{R_0} &= \frac{A}{\left|2A-B^2\right|^{1/2}}\\
%\tan\theta_c &= \frac{2A-B^2}{\left|B^2 - 2A\right|^{1/2}} \label{eq:thc-conic} \\
%\mathrm{where:~} B &\equiv \frac{R_{90}}{R_0} \\
%#A &\equiv \frac{R_c}{R_0}
%\end{align}
